Deconvolution to FANS4

### 2020-08-26 deconvolution/apply_dtangle_FANS4.Rmd
add upload

# TMM normalization
geneExpr = DGEList( as.matrix(geneCounts))
geneExpr = calcNormFactors(geneExpr)
geneExpr_logCPM = cpm(geneExpr, log=TRUE)

@@

### Data preprocessing
```{r preprocess.data}
synId_covariates = c('syn21862454', 'syn21887888', 'syn21825507') # 'syn21888968'

@@

nEXP_OBJ = File(file, 
                name = 'Estimates from dtangle', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)
```

>>>>

# TMM normalization
geneExpr = DGEList( as.matrix(geneCounts))
geneExpr = calcNormFactors(geneExpr)
geneExpr_logCPM = edgeR::cpm(geneExpr, log=TRUE)

@@

### Data preprocessing
```{r preprocess.data}
synId_covariates = c('syn21862454', 'syn21887888', 'syn21825507') # 'syn21888968'
ALL_USED_IDs = c(ALL_USED_IDs, synId_covariates)

@@

nEXP_OBJ = File(file, 
                name = 'Estimates from dtangle', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = ALL_USED_IDs, 
                    executed = thisFile)
```
